---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# xaringanPrinter

<!-- badges: start -->
[![Lifecycle: deprecated](https://img.shields.io/badge/lifecycle-deprecated-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#deprecated)
<!-- badges: end -->

The goal of xaringanPrinter is to provide an easy interface to convert xaringan (remark.js) slides to other formats.

remark.js slides aren't self contained, and sometimes it's not ideal, so you might want to convert of pdf.  The function slides_pdf is just a wrapper for chrome_print from pagedown.

You might also want a gif preview of slides.  You can do this with slides_gif().  Under the hood, we do this by converting html slides to pdf, then the pdf pages to images, and the images to a gif.  



## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
remotes::install_github("EvaMaeRey/xaringanPrinter")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval = FALSE}
library(xaringanPrinter)
## basic example code
```


```{r cars, eval = F}
slides_gif(input = "my_slideshow.html", output = "a_folder/my_slideshow.gif")
```

This will produce "my_slideshow.gif" in "a_folder".

# Deprecated

This package is no longer being developed. Current work regarding outputting `{xaringan}` slides into different formats has coalesced around [Jhelvy/xaringanBuilder](https://github.com/jhelvy/xaringanBuilder).
